---
title: "Data Science 2,Hw1"
author: "Ekta Chaudhary"
date: "24/02/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(message = F)
```

```{r}
library(tidyverse)
library(caret)
library(ModelMetrics)
library(glmnet)
```

# Reading the Datasets 

```{r}
train_data = read_csv(file = "./data/solubility_train.csv")
test_data = read_csv(file = "./data/solubility_test.csv")
```

We will predict solubility of compounds using their chemical structures.The  training  data  are  in  the  file  “solubilitytrain.csv”  and  the  test  data  are  in  “solubil-itytest.csv”.  Among the 228 predictors, 208 are binary variables that indicate the presenceor absence of a particular chemical substructure, 16 are count features, such as the numberof bonds or the number of bromine atoms, and 4 are continuous features, such as molecularweight or surface area.  The response is in the column “Solubility”.

# Linear Model

```{r}
fit_lm <- lm(Solubility~., data = train_data)
pred_lm <- predict(fit_lm, test_data)
mse(test_data$Solubility, pred_lm)
```

```{r}
x <- model.matrix(Solubility~.,test_data)[,-1]
# vector of response
y <- test_data$Solubility
ridge.mod <- glmnet(x,y, standardize = TRUE,
                    alpha = 0, 
                    lambda = exp(seq(-1, 10, length = 100)))
```

```{r}
mat.coef <- coef(ridge.mod)
dim(mat.coef)
```

```{r}
set.seed(2)
cv.ridge <- cv.glmnet(x, y, type.measure = "mse",
                      alpha = 0, 
                      lambda = exp(seq(-1, 10, length = 100)))

plot(cv.ridge)
```
```{r}
best.lambda <- cv.ridge$lambda.min
best.lambda
```

```{r}
best.lambda <- cv.ridge$lambda.min
best.lambda
cv.ridge
predict(ridge.mod, s = best.lambda, type="coefficients")
# predict(cv.ridge, s = best.lambda, type="coefficients") 
# predict(cv.ridge, s = "lambda.min", type="coefficients") 
# predict(cv.ridge, s = "lambda.1se", type="coefficients") 
```

