---
title: "Data Science 2,Hw1"
author: "Ekta Chaudhary"
date: "24/02/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = F)
knitr::opts_chunk$set(message = F)
```

```{r}
library(tidyverse)
library(caret)
library(ModelMetrics)
library(glmnet)
```

# Reading the Datasets 

```{r}
train_data = read_csv(file = "./data/solubility_train.csv")
test_data = read_csv(file = "./data/solubility_test.csv")
```

We will predict solubility of compounds using their chemical structures.The  training  data  are  in  the  file  “solubilitytrain.csv”  and  the  test  data  are  in  “solubil-itytest.csv”.  Among the 228 predictors, 208 are binary variables that indicate the presenceor absence of a particular chemical substructure, 16 are count features, such as the numberof bonds or the number of bromine atoms, and 4 are continuous features, such as molecularweight or surface area.  The response is in the column “Solubility”.

# Linear Model

```{r}
fit_lm <- lm(Solubility~., data = train_data)
pred_lm <- predict(fit_lm, test_data)
mse(test_data$Solubility, pred_lm)
```
# Ridge Regression 

```{r}
x <- model.matrix(Solubility~.,test_data)[,-1]
# vector of response
y <- test_data$Solubility
ridge.mod <- glmnet(x,y, standardize = TRUE,
                    alpha = 0, 
                    lambda = exp(seq(-1, 10, length = 100)))
```

```{r}
ctrl1 <- trainControl(method = "repeatedcv", number = 10, repeats = 5)

set.seed(2)
ridge.fit <- train(x, y,
                   method = "glmnet",
                   tuneGrid = expand.grid(alpha = 0, 
                                          lambda = exp(seq(-10, 10, length = 200))),
                   # preProc = c("center", "scale"),
                   trControl = ctrl1)

plot(ridge.fit, xTrans = function(x) log(x))
```
```{r}
ridge.fit$bestTune
best_lambda <- ridge.fit$bestTune$lambda
best_lambda
```


#Lasso 

```{r}
set.seed(2)
lasso.fit <- train(x, y,
                   method = "glmnet",
                   tuneGrid = expand.grid(alpha = 1, 
                                          lambda = exp(seq(-10, 10, length = 200))),
                   # preProc = c("center", "scale"),
                   trControl = ctrl1)

plot(lasso.fit, xTrans = function(x) log(x))
```


```{r}
lasso.fit$bestTune
best_lambda_lasso <- lasso.fit$bestTune$lambda
best_lambda_lasso
```




